Estimating Real-Time Highstreet Footfall from Wi-Fi Probe Requests

### 2018-12-06 paper/sections/main_study.tex
main study changes

We start by looking at the distribution of the signal strength reported by the
probe requests across the locations. From the density plot shown in Figure
\ref{main_signal_strength} we can see that there is clear relation between the
distribution of the signal strength and the distance and complexity of the
source of noise. We can see that while location 5 shows clean difference between
low and high signal strengths, location 2 is almost normally distributed.
Intuitively we expect that location 2 and 4 must be harder to classify than
location 1 3 and 5.  We run the k-means clustering algorithm and filter out the
probe requests which are randomised and have signal strengths less than the
second break (threshold).  It is important to note that we are dealing with
relative thresholds of signal strengths which can vary with location and time of
the analysis.  We then aggregate then probe requests for every minute by
counting the number of Unique MAC addresses present in every minute. We also
remove devices that dwell around the sensor by removing the MAC addresses which
reappear from within the past hour.  The results of the first stage of filtering
process along with the thresholds are shown in Table \ref{errors_table}.
Confirming our intuition, we see that the location 2 has the most MAPE followed
by location 4 while rest of them have highly reduced MAPE.  It is significant
that this method alone reduces our margin of error by a 50 - 100\% from the raw
counts without any cleaning.  This makes the signal strength filtering quick and
ideal method for practical applications which doesn't require absolute numbers
such as creating large aggregated indexes to show long term trends.  We also see
that the success of the signal strength filtering can be improved significantly
by installing sensors such that the pedestrians and noise are at different
distances from the sensor and are the field of measurement is distinct from the
surroundings however noisy it might be.

>>>>

We begin by looking at the distribution of the signal strength reported by the
probe requests across the locations. From the density plot shown in Figure
\ref{main_signal_strength}, we can observe that there is clear relation between
the distribution of the signal strength and the distance and complexity of the
source of noise. We can see that while location 5 shows clean difference
between low and high signal strengths, location 2 is almost normally
distributed.  Intuitively we expected that location 2 and 4 would be harder to
classify than locations 1, 3 and 5.  We ran the k-means clustering algorithm
and filtered out the probe requests which were randomised and had signal
strengths less than the second break (threshold).  It is important to note that
we were dealing with relative thresholds of signal strengths which can vary
with location and time of the analysis.  We then aggregated the probe requests
by counting the number of Unique MAC addresses present in every minute. We also
removed devices that dwelled around the sensor by removing the MAC
addresses which reappeared within the previous hour.

The results of the first stage of the filtering process along with the
thresholds are shown in Table \ref{errors_table}.  Confirming our intuition, we
see that the location 2 has the most MAPE followed by location 4 while rest of
them have highly reduced MAPE.  It is significant that this method alone
reduces our margin of error by a 50 - 100\% from the raw counts without any
cleaning.  This makes the signal strength filtering quick and ideal method for
practical applications which doesn't require absolute numbers such as creating
large aggregated indexes to show long term trends.  We also see that the
success of the signal strength filtering can be improved significantly by
installing sensors such that the pedestrians and noise are at different
distances from the sensor and are the field of measurement is distinct from the
surroundings however noisy it might be.
